Prelim Outline

### 2019-05-31 outline.tex
really rough outline, send to lucas for comments

\documentclass{article}
\title{Prelim Outline}
\author{Shivesh Pathak}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\begin{document}

\section{Introduction and methods}
\textit{The goal of the introduction is to show the reader that the project is valuable. Should be x pages, other 5-x page will be methods.}

\paragraph{Overall goal} We want to be able to systematically develop low-energy effective models for strongly correlated electron systems.

@@

\paragraph{Current state of the art} ??

\paragraph{Advancement to the state of the art} We propose using a density matrix downfolding (DMD) procedure to develop low-energy effective theories of the 1-band nearest-neighbor Hubbard model on a square lattice as a stepping stone towards usage on \textit{ab-initio} Hamiltonians of strongly correlated materials.

@@

\pagebreak

@@

\paragraph{CuO: Methods} In order to fit a model using DMD we had to construct a low energy space (LES), choose a sampling scheme for states within the LES resulting in our sample space (SS), and develop a basis which can accurately describe variations within the LES.

@@

\paragraph{Hubbard: Preliminary results} Our preliminary calculations on the 2x2 1-band Hubbard model at half-filling indicate the emergence of a gapped low-energy subspace for U/t $\ge$ 10 described well by a nearest neighbor Heisenberg model, and a set of models with 0 $<$ U/t $\leq$ 4 which are poorly described by either a non-interacting fermion or Heisenberg model.

\section{Proposed work}
\paragraph{Hubbard stuff?}

\section{Conclusion and Summary}

>>>>

\documentclass{article}
\title{Prelim Outline}
\author{Shivesh Pathak}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\begin{document}

\section{Introduction and methods}
\paragraph{Overall goal} We want to be able to systematically develop low-energy effective models for strongly correlated electron systems.

@@

\paragraph{Current state of the art} \textcolor{red}{Talk about methods people use for model fitting now. Will fill out as I do literature review.}

\paragraph{Advancement to the state of the art} We propose using a density matrix downfolding (DMD) procedure to develop low-energy effective theories of the 1-band nearest-neighbor Hubbard model on a square lattice as a stepping stone towards effective theories starting from \textit{ab-initio} Hamiltonians of strongly correlated materials.

@@

@@

\paragraph{CuO: Methods} In order to fit a model using DMD we had to construct a low energy space (LES), choose a sampling scheme for states within the LES resulting in our sample space (SS), develop a basis which can accurately describe variations within the LES, identify and select descriptors built out of these basis elements, and appropriately fit the data from our SS onto our selected descriptors.

@@

\paragraph{Hubbard: Preliminary results} Our preliminary calculations on the 2x2 half-filled 1-band Hubbard model map out the limiting behavior in the U-T model space by investigating the effectiveness of the single descriptor models.

\section{Proposed work}
\paragraph{Hubbard: Effective models at half-filling} We want to develop low-energy effective theories for the half-filled Hubbard model over the space U: 0 - 12, 1/$k_B$T: 0 - 3, particularly on the medium coupling region of U: 2 - 6 and 1/$k_B$T $\sim$ 1 where perturbative effective theories seem to break down.

\paragraph{Hubbard: Effective models away from half-filling} A farther reaching goal would be to develop effective theories in the U-T-$\delta$ space, where more complex behavior similar to the cuprates have been found.

\paragraph{Hubbard: Finite size effects} Our initial calculations can be done using exact diagonalization, but memory limitations will require us to use approximate quantum Monte Carlo methods to calculate energies and density matrix elements for states in our LES.

\section{Proposed timeline}
\textit{Do this after proposed work nailed down}.
